### 2014-05-21 remy_limits.tex
control service -> control surface

\begin{figure}
\caption{Ratatouille allows a user to vary network conditions on a
  physical control service, then observe the resulting behavior of a
  RemyCC in real-time. Below, the initial startup and steady-state
  behavior of the RemyCC-100x algorithm of Section~\ref{s:oprangeperftradeoff}.}
\label{fig:ratscreen}

>>>>

\begin{figure}
\caption{Ratatouille allows a user to vary network conditions on a
  physical control surface, then observe the resulting behavior of a
  RemyCC in real-time. Below, the initial startup and steady-state
  behavior of the RemyCC-100x algorithm of Section~\ref{s:oprangeperftradeoff}.}
\label{fig:ratscreen}
